---
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir="~/Documents/Andrea/LesFlick/data_reporting/",echo = FALSE, fig.width=7, fig.height=10)
file_path <- "data/test/tweet_activity_metrics_LesFlicks_20200201_20200301_en.csv"
output_path <- "output/2020_05_25/"
```

## Report content
Some text...

```{r set_up}
source('src/utils.R')
title_var <- "Twitter Data Analysis"
twitter_data <- get_data(file_path)
date_range <- get_date_range(twitter_data)
subtitle_var <- paste("Period: ", date_range, collapse = "")
```
---
title: `r title_var`
subtitle: `r date_range`
date: `r format(Sys.Date(), format="%d %B %Y")`
---

## Summary
* There were **`r nrow(twitter_data)`** Tweets this month
* The average number of Tweets was `r format(mean(table(twitter_data$date)), digits = 4)` ranging from `r format(min(table(twitter_data$date)))` to `r format(max(table(twitter_data$date)))` Tweets per day.

### Top 5 url clicks

### Top 5 impressions 

### Top 5 engagements

<!-- TODOS 20200526  -->
<!-- Add summary info  -->
<!-- How many tweets  --
<!-- Average number of tweets per day  -->
<!-- Max number of tweets in a day  -->
<!-- Include Top 5 url clicks  -->
<!-- Include Top 5 impressions table  -->
<!-- Include Top 5 engagements table  -->
<!-- Add Mentions and impressions plot  -->
<!-- Find out meaning of media views and media engagement  -->
<!-- Bottom XX  -->
<!-- Engagements  -->
<!-- Media views   -->
<!-- etc  -->
<!-- MAKE TOP X var  -->
<!-- Summary version (top 5 XX) AND detailed version (top YY)  -->
<!-- PLOTS  -->
<!-- x: average number of messages per hour   -->
<!-- y: average impressions / engagements  -->
<!-- facet: per day  -->
<!-- Find out if retweets are included in data   -->

## impressions_by_day_time
Some plots... Note the difference in the y-axis values.

```{r impressions_plot, fig.height = 7, fig.width = 7}
p <- plot_impressions_by_day_time(twitter_data, output_path)
print(p)
```

## hashtags cliks
```{r hastag_plot, fig.height = 7, fig.width = 7}
p2 <- plot_hashtags(twitter_data, output_path)
print(p2)
```

## numbers
Some tables
```{r tables, results = 'asis'}
out <- get_top_quantitative(twitter_data)
for(o in out){ 
  print(knitr::kable(o, row.names = FALSE, align = "l"), caption = "\n")
  }
# knitr::kable(out[[1]], row.names = FALSE, align = "l")
```

